---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The `logisticReg` package provides a custom implementation of logistic regression using Iteratively Reweighted Least Squares (IRLS). In this vignette, we will demonstrate how to use the `logistic_reg` function and compare it to the `glm` function from base R to validate the correctness and efficiency.

## Example Usage

First, let's simulate some data to fit a logistic regression model.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(logisticReg)
```

```{r}
set.seed(123)
X <- cbind(1, matrix(rnorm(100), ncol = 2))
y <- rbinom(50, 1, prob = 0.5)
```

Fitting Logistic Regression with logistic_reg We will fit a logistic regression model using the logistic_reg function.
```{r}
library(logisticReg)
logistic_result <- logistic_reg(X, y)
print(logistic_result$coefficients)

```

## Comparison with glm
Now, let's fit the same model using the glm function and compare the coefficients with logistic_reg.
```{r}
glm_result <- coef(glm(y ~ X[, -1], family = binomial))
print(glm_result)
```

## Correctness Comparison

We use `all.equal()` to verify if the coefficients estimated by `logistic_reg` match those of `glm`. To account for possible numerical differences in the algorithms, we include a tolerance level.

```{r compare-results}
correctness_check <- all.equal(
  round(logistic_result$coefficients, 4), 
  round(glm_result, 4),
  tolerance = 1e-4
)
print(correctness_check)
```
The output should indicate that the coefficients from logistic_reg are very close to those from glm, indicating that the implementation is correct.

## Efficiency Comparison
We will use the bench::mark package to compare the performance of logistic_reg and glm. This will help us understand the efficiency of our implementation compared to the standard glm function.
```{r}
library(bench)

benchmark_result <- bench::mark(
  logistic_reg = logistic_reg(X, y)$coefficients,
  glm = coef(glm(y ~ X[, -1], family = binomial)),
  iterations = 100
)
print(benchmark_result)
```
## Conclusion
In this vignette, we demonstrated how to use the logistic_reg function from the logisticReg package and compared it to the standard glm function. The results showed that:

### Correctness: The coefficients estimated by logistic_reg are very similar to those from glm, indicating that the implementation is correct.

### Efficiency: We also benchmarked the functions to assess their efficiency, which provides insight into the performance of our implementation compared to the standard glm function.
